Writing a reproducible paper in Pagedown^[Corresponding address: mail@paulcbauer.eu.<br> Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]

### 2021-06-20 paper_pagedown.Rmd
added a date class to the front page (wp_paged.html) and modified its size and appearance (jss.css).

---
title: "Writing a reproducible paper in Pagedown^[Corresponding address: mail@paulcbauer.eu.<br> Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]"
shorttitle: "Writing a reproducible paper in Pagedown"
author:
  - name: Paul C. Bauer
    affiliation: Mannheim Centre for European Social Research
    email: <mail@paulcbauer.eu>
  - name: Camille Landesvatter
    affiliation: Mannheim Centre for European Social Research
    email: <landesvatterc@gmail.com>
date: |
  |       
  | Based on: https://osf.io/q395s
  | This version: `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
  |
  | Feedback? Errors?
  | mail@paulcbauer.eu
  | [Github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)
abstract: 'The present paper provides a template for a reproducible scientific paper written in R Markdown. Below I outline some of the "tricks"/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). I intend to update this file when I discover more convenient code (you can follow any updates through the corresponding [github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).'
# at least one keyword must be supplied
keywords: [keywords]
links-to-footnotes: true
paged-footnotes: true
bibliography: index.bib
output: 
  pagedown::jss_paged:
    self_contained: false
    css: ['jss.css', 'jss-fonts.css', 'jss-page.css']
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
---

>>>>

---
title: "Writing a reproducible paper in Pagedown^[Corresponding address: mail@paulcbauer.eu.<br> Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]"
shorttitle: "Writing a reproducible paper in Pagedown"
author:
  - name: Paul C. Bauer
    affiliation: Mannheim Centre for European Social Research
    email: <mail@paulcbauer.eu>
  - name: Camille Landesvatter
    affiliation: Mannheim Centre for European Social Research
    email: <landesvatterc@gmail.com>
date: 'First version: 2 December, 2019<br>This version: `r format(Sys.time(), "%d %B, %Y")`'
abstract: 'The present paper provides a template for a reproducible scientific paper written in R Markdown. Below I outline some of the "tricks"/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). I intend to update this file when I discover more convenient code (you can follow any updates through the corresponding [github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).'
# at least one keyword must be supplied
keywords: [keywords]
links-to-footnotes: true
paged-footnotes: true
bibliography: index.bib
output: 
  pagedown::jss_paged:
    template: wp_paged.html
    self_contained: false
    css: ['jss.css', 'jss-fonts.css', 'jss-page.css']
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
---
